PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected data group chunks for PHQ, GAD, PCL

#Data level groups
Identify which data (prepan, retro and baseline) each participant has.
++KT: not sure how best to categorise here so this may need some revision. 
```{r data level groups}
dat.glad <- dat.glad %>%
  mutate(
    data_group_full_numeric =
      case_when(
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0  & na_per_person_gad_retro == 0 & na_per_person_pcl_retro == 0 ~ 5,
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_pcl_retro == 0 ~ 4, #in GLAD, in COPING and have no missing PCL-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_gad_retro == 0 ~ 3, #in GLAD, in COPING and have no missing GAD-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0 ~ 2, #in GLAD, in COPING and have no missing PHQ-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) ~ 1,
        !is.na(startDate.glad) & is.na(startDate.coping.glad) ~ 0
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    data_group_full = 
      recode_factor(
        data_group_full_numeric,
        "0" = "Only prepandemic data",
        "1" = "Prepandemic and baseline data",
        "2" = "Prepandemic, baseline and retrospective PHQ data",
        "3" = "Prepandemic, baseline and retrospective GAD data",
        "4" = "Prepandemic, baseline and retrospective PCL data",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat.glad$data_group_full)
```

>>>>

#Data level groups
Identify which data (prepan, retro and baseline) each participant has.
```{r data level groups PHQ}
dat.glad <- dat.glad %>%
  mutate(
    data_group_phq_numeric =
      case_when(
        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
        na_per_person_phq_base != 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0 ~ 1,  #baseline and retro data only
        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    data_group_phq = 
      recode_factor(
        data_group_phq_numeric,
        "0" = "Only prepandemic data",
        "1" = "Baseline and retrospective data",
        "2" = "Prepandemic and baseline data",
        "3" = "Baseline data only",
        "4" = "Retrospective data only",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat.glad$data_group_phq)
```

GAD
```{r data level groups GAD}
dat.glad <- dat.glad %>%
  mutate(
    data_group_gad_numeric =
      case_when(
        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
        na_per_person_gad_base != 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0 ~ 1,  #baseline and retro data only
        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    data_group_gad = 
      recode_factor(
        data_group_gad_numeric,
        "0" = "Only prepandemic data",
        "1" = "Baseline and retrospective data",
        "2" = "Prepandemic and baseline data",
        "3" = "Baseline data only",
        "4" = "Retrospective data only",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat.glad$data_group_gad)
```

PCL
```{r data level groups PCL}
dat.glad <- dat.glad %>%
  mutate(
    data_group_pcl_numeric =
      case_when(
        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0 ~ 1,  #baseline and retro data only
        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    data_group_pcl = 
      recode_factor(
        data_group_pcl_numeric,
        "0" = "Only prepandemic data",
        "1" = "Baseline and retrospective data",
        "2" = "Prepandemic and baseline data",
        "3" = "Baseline data only",
        "4" = "Retrospective data only",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat.glad$data_group_pcl)
```
